EDA of DSRCT Samples

### 2024-10-15 analyses/cell-type-dsrct/exploratory_analysis/01-marker-gene-tumor-classification.Rmd
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

```{r paths}
sce_file_list <- list()
for (i in 1:dim(metadata_DSRCT)[1])
{
  # Input files
  sce_file <- paste0(metadata_DSRCT$scpca_library_id[i], '_processed.rds')
  sce_file_list[[i]] <- file.path(data_dir, "SCPCP000013", metadata_DSRCT$scpca_sample_id[i], sce_file)
}

@@

Read in each data as a separate object `SingleCellExperiment` in the list. 
```{r}
sce_list <- lapply(sce_file_list, function(x){
  # read in processed sce
  sce <- readr::read_rds(x)
})

#adding the sample id to the name of each SingleCellExperiment
names(sce_list) <- metadata_DSRCT$scpca_sample_id

>>>>

```{r paths}
sce_file_list <- file.path(
  data_dir, "SCPCP000013",  
  metadata_DSRCT$scpca_sample_id, 
  paste0(metadata_DSRCT$scpca_library_id, "_processed.rds")
)

@@

Read in each data as a separate object `SingleCellExperiment` in the list. 
```{r}
sce_list <- lapply(sce_file_list, readr::read_rds)

#adding the sample id to the name of each SingleCellExperiment
names(sce_list) <- metadata_DSRCT$scpca_library_id
